### 2023-05-31 paper/content.tex
Fix non-dipolarity figure paths
Remove the leading "paper/". Don't know why Overleaf is fine with this
but it fails to compile locally.

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{paper/figures/non-dipolarity-synthetic.png}
  \caption{Caption: Simulated magnetic microscopy data for a spherical source with both dipolar and non-dipolar magnetic components. The distance from the sensor varies from 1 µm to 6 µm (a-f).}
  \label{non-dipolarity-synthetic-data}
\end{figure}

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{paper/figures/non-dipolarity-synthetic-positioning.png}
  \caption{The simulation was randomly replicated (N=100) to test the effectiveness of the Euler deconvolution in estimating the position of the modeled particles. The difference between the true position (centroid) and the estimated position was calculated for each replicate and plotted as a boxplot. The boxplot shows the distribution of differences in the (a) $x_c$, (b) $y_c$, and (c) $z_c$.}
  \label{non-dipolarity-synthetic-data-positioning}
\end{figure}

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{paper/figures/non-dipolarity-synthetic-inversion.png}
  \caption{The simulation was randomly replicated (N=100) to assess the accuracy of the algorithm in recovering the magnetic direction and moment of the modeled particles. The goodness of fit was measured by the R-squared value (a), while the angular error (b) and intensity error (c) between the real and modeled magnetic vector were plotted in degrees and percentages ($|100 \left( m_{true} - m_{estimated}\right) ~/~ m_{true}|$), respectively.}
  \label{non-dipolarity-synthetic-data-inversion}
\end{figure}

>>>>

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/non-dipolarity-synthetic.png}
  \caption{Caption: Simulated magnetic microscopy data for a spherical source with both dipolar and non-dipolar magnetic components. The distance from the sensor varies from 1 µm to 6 µm (a-f).}
  \label{non-dipolarity-synthetic-data}
\end{figure}

@@

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/non-dipolarity-synthetic-positioning.png}
  \caption{The simulation was randomly replicated (N=100) to test the effectiveness of the Euler deconvolution in estimating the position of the modeled particles. The difference between the true position (centroid) and the estimated position was calculated for each replicate and plotted as a boxplot. The boxplot shows the distribution of differences in the (a) $x_c$, (b) $y_c$, and (c) $z_c$.}
  \label{non-dipolarity-synthetic-data-positioning}
\end{figure}

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/non-dipolarity-synthetic-inversion.png}
  \caption{The simulation was randomly replicated (N=100) to assess the accuracy of the algorithm in recovering the magnetic direction and moment of the modeled particles. The goodness of fit was measured by the R-squared value (a), while the angular error (b) and intensity error (c) between the real and modeled magnetic vector were plotted in degrees and percentages ($|100 \left( m_{true} - m_{estimated}\right) ~/~ m_{true}|$), respectively.}
  \label{non-dipolarity-synthetic-data-inversion}
\end{figure}
